{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
Small change, structure

	\paragraph{Monomial Basis}
	{\color{red} No shift parameter in implementation in fda.} The Monomial basis are trivially decompositions of every polynomial function.

	For functions that fall into the class of entire functions, we can express the function as a potentially infinite sum of weighted monomials. Let $f(t)$ be an entire function, e.g. the exponential function or a trigonometric function, then we can write the following.

>>>>

	\paragraph{Monomial Basis}
	The Monomial basis are trivially decompositions of every polynomial function. {\color{red} Continue Work here!}	
	For functions that fall into the class of entire functions, we can express the function as a potentially infinite sum of weighted monomials. Let $f(t)$ be an entire function, e.g. the exponential function or a trigonometric function, then we can write the following.
